Temperature Effects on Surface Sulfur Dioxide

### 2011-07-26 Background.tex
Finished adding images for rough draft round 1

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/double-cycle-type2-small.png}
		\caption{}
		\label{fig:cyclic-example}
	\end{center}
\end{figure}

@@

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/cycle-types-small.png}
		\caption{}
		\label{fig:cyclic-structures}
	\end{center}
\end{figure}

@@

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/triple-cycle-types-small.png}
		\caption{}
		\label{fig:type-3-varieties}
	\end{center}
\end{figure}

>>>>

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/cycles/double-cycle-type2-small.png}
		\caption{}
		\label{fig:cyclic-example}
	\end{center}
\end{figure}

@@

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/cycles/cycle-types-small.png}
		\caption{}
		\label{fig:cyclic-structures}
	\end{center}
\end{figure}

@@

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/cycles/triple-cycle-types-small.png}
		\caption{}
		\label{fig:type-3-varieties}
	\end{center}
\end{figure}

### 2011-07-26 Coordination-Results.tex
Filling in the images
Finished adding images for rough draft round 1

@@

The binding behavior of the \suldiox~is altered by changing the temperature of the system, as evidenced in the shift in coordination populations of Figure \ref{fig:bonding-coordinations} from cold to hot. In the cold temperature, the unbound, single oxygen, and ``S'' coordinations are more populated than in the hot systems. The increased temperature causes all the coordinations with a single sulfur interaction or more (with the exception of ``S'') to increase over the equivalent cold temperature coordination populations. We see that the cold \suldiox~spends nearly twice as much time unbound, and only slightly more time in the ``S'' coordination. Most of the unbound population in the hot simulations appears to have shifted to the states with double-oxygen and double-sulfur coordinations. Figure \ref{fig:coordination-breakdown} shows the distribution of the number of bonds through the \suldiox~oxygens (left) and through the \suldiox~sulfur (right). When comparing from cold to hot distributions, the greatest shift occurs in the number of \suldiox~oxygen bonds as the hot \suldiox~has more multiply-bound oxygens (double and triple interactions). The increased temperature allows the \suldiox~oxygens to bind to more water hydrogens than in the cold systems.

These increased binding through the \suldiox~oxygens at the hot temperatures should have a visible effect on the radial distribution function (RDF) between \suldiox-oxygen and water-hydrogen. Figure \ref{fig:rdf} shows the RDF of the \suldiox~sulfur and oxygen atoms with their water bonding partners, water oxygen and hydrogen, respectively, at both cold and hot temperatures. Both the first and second peaks of the O$_{SO_2}$-H$_{H_2O}$ RDF increase at the higher temperature, indicating a large number of water hydrogens near the \suldiox~oxygens in both hydration shells. This corroborates the increased coordination through the \suldiox~oxygens to the surface waters at the higher temperature.

>>>>

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/coordinations/so2-coordinations-percents-small.png}
		\caption{}
		\label{fig:bonding-coordinations}
	\end{center}
\end{figure}

@@

The binding behavior of the \suldiox~is altered by changing the temperature of the system, as evidenced in the shift in coordination populations of Figure \ref{fig:bonding-coordinations} from cold to hot. In the cold temperature, the unbound, single oxygen, and ``S'' coordinations are more populated than in the hot systems. The increased temperature causes all the coordinations with a single sulfur interaction or more (with the exception of ``S'') to increase over the equivalent cold temperature coordination populations. We see that the cold \suldiox~spends nearly twice as much time unbound, and only slightly more time in the ``S'' coordination. Most of the unbound population in the hot simulations appears to have shifted to the states with double-oxygen and double-sulfur coordinations. Figure \ref{fig:coordination-breakdown} shows the distribution of the number of bonds through the \suldiox~sulfur (top) and through the \suldiox~oxygens (bottom). When comparing from cold to hot distributions, the greatest shift occurs in the number of \suldiox~oxygen bonds as the hot \suldiox~has more bonding to the oxygens. The increased temperature allows the \suldiox~oxygens to bind to more water hydrogens than in the cold systems.

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/coordinations/coordination-breakdown-small.png}
		\caption{}
		\label{fig:coordination-breakdown}
	\end{center}
\end{figure}

These increased binding through the \suldiox~oxygens at the hot temperatures should have a visible effect on the radial distribution function (RDF) between \suldiox-oxygen and water-hydrogen. Figure \ref{fig:rdf} shows the RDF of the \suldiox~sulfur and oxygen atoms with their water bonding partners, water oxygen and hydrogen, respectively, at both cold (blue) and hot (green) temperatures. Both the first and second peaks of the O$_{SO_2}$-H$_{H_2O}$ RDF increase at the higher temperature, indicating a large number of water hydrogens near the \suldiox~oxygens in both hydration shells. This corroborates the increased coordination through the \suldiox~oxygens to the surface waters at the higher temperature.

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/rdf/rdf-small.png}
		\caption{}
		\label{fig:rdf}
	\end{center}
\end{figure}
